Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact

### 2019-09-04 tse19/main.tex
added script

The projects with flakiness
in all configurations were \CodeIn{Activity}, \CodeIn{Incubator Dubbo}, \CodeIn{DROID}, and
\CodeIn{Hawkbit}.  It is worth highlighting the unfortunate case of
\CodeIn{Hawkbit}, which manifested more than 9\% flaky tests in
every configuration.  Considering time, it is noticeable from the
averages, perhaps as expected, an increasing speedup from
configuration \emph{\SeqClassParMeth} to \emph{\ParClassParMeth} and
from configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.  It is also
worth mentioning that some combinations manifested slowdown instead of
speedup.  Recall that parallel execution introduces the overhead of
spawning and managing JVMs and threads.  Overall, results show that
0\% of flakiness have been reported in 47 of the 105 (=5x15)
pairs of project and configuration we analyzed (44.76\% of the total).
In for 6 of the 21 projects flakiness was not manifested in 
any combination pairs.  We noticed with some surprise that the average speedup of
configuration \emph{\SeqClassParMeth} was higher compared to \emph{\ParClassSeqMeth} and \emph{\ParClassParMeth},
indicating that it is not always the case that
using more CPUs pays off. Important to note that the cost of spawning
new JVMs can be significant in \emph{\ForkParMeth}.

>>>>

The projects with flakiness
in all configurations were \CodeIn{Activity}, \CodeIn{Incubator Dubbo}, \CodeIn{DROID}, and
\CodeIn{Hawkbit}.  It is worth highlighting the unfortunate case of
\CodeIn{Hawkbit}, which manifested more than 9\% flaky tests in
every configuration.  Considering time, it is noticeable from the
averages, perhaps as expected, an increasing speedup from
configuration \emph{\SeqClassParMeth} to \emph{\ParClassParMeth} and
from configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.  It is also
worth mentioning that some combinations manifested slowdown instead of
speedup.  Recall that parallel execution introduces the overhead of
spawning and managing JVMs and threads.  Overall, results show that
0\% of flakiness have been reported in 47 of the 105 (=5x21)
pairs of project and configuration we analyzed (44.76\% of the total).
In for 6 of the 21 projects flakiness was not manifested in 
any combination pairs.  We noticed with some surprise that the average speedup of
configuration \emph{\SeqClassParMeth} was higher compared to \emph{\ParClassSeqMeth} and \emph{\ParClassParMeth},
indicating that it is not always the case that
using more CPUs pays off. Important to note that the cost of spawning
new JVMs can be significant in \emph{\ForkParMeth}.
